Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-12-03 Manuscript.Rmd
Added note on the usefulness of the sliding window analysis
Temp visualizations comparing FValues across communities per subject

@@

# To get the rate of stability per vertex across subjects
FB <- do.call(cbind, lapply(Summaries, "[[", "FiedlerBinary"))
FBS <- rowMeans(FB)
FBS[FBS < 0.5] <- 1 - FBS[FBS < 0.5]

# Now let's test something: 
# Traditionally, a vertex-wise test would be carried across subjects.
# If these traditional analyses miss out on these idiosyncrasies, you should get unsignificant results.
# So we did a prop.test per vertex, and corrected with FDR to mimic this situation.
All_proptests <- apply(FB, 1, function(x) {prop.test(sum(x), nSubj)})
Pvals_corrected <- p.adjust(sapply(All_proptests, "[[", "p.value"), method = "BY")
Chisquares <- sapply(All_proptests, "[[", "statistic")
```

@@

>>>>

  # NOTES:
  # you can apply pairwise comparisons with outer: outer(tempList,tempList,FUN = Vectorize(arandi, SIMPLIFY = FALSE, USE.NAMES = FALSE))

@@

# To get the rate of stability per vertex across subjects
FB <- do.call(cbind, lapply(Summaries, "[[", "FiedlerBinary"))
FV <- do.call(cbind, lapply(Summaries, "[[", "FiedlerVec"))
FBS <- rowMeans(FB)
FBS[FBS < 0.5] <- 1 - FBS[FBS < 0.5]

# Now let's test something: 
# Traditionally, a vertex-wise test would be carried across subjects.
# If these traditional analyses miss out on these idiosyncrasies, you should get unsignificant results.
# So we did a prop.test per vertex, and corrected with FDR to mimic this situation.
All_proptests <- apply(FB, 1, function(x) {prop.test(sum(x), nSubj)})
Prop_pvals_corrected <- p.adjust(sapply(All_proptests, "[[", "p.value"), method = "BY")
Prop_pvals_corrected <- ifelse(Prop_pvals_corrected < 0.05, 1, 0)
Chisquares <- sapply(All_proptests, "[[", "statistic")

# And a t-test on the FV vals
All_ttests <- apply(FV, 1, t.test)
Ttest_pvals_corrected <- p.adjust(sapply(All_ttests, "[[", "p.value"), method = "BY")
Ttest_pvals_corrected <- ifelse(Ttest_pvals_corrected < 0.05, 1, 0)
Tstats <- sapply(All_ttests, "[[", "statistic")

### Testing grounds
# this part compares the distribution of Fiedler values for DMN and nonDMN
# note: remove filter(y > 0) for 'full brain'
# First plot compares the median FV between communities across subjects
test <- do.call(rbind, Summaries)
test %>%
  mutate(SubjID = rep(subjList, each = 5081),
         FV_abs = abs(FiedlerVec),
         Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
  filter(y > 0) %>%
  group_by(SubjID, Community) %>%
  summarize(FV_mean = median(FV_abs)) %>%
  ggplot(aes(Community, FV_mean)) +
  geom_boxplot() + 
  theme_classic()
# Second one plots the ecdf
# Line indicates the 75th quantile of the combined Fiedler vectors across participants (i.e. potential threshold)
test %>%
  mutate(SubjID = rep(subjList, each = nrow(Summaries[[1]])),
         FV_abs = abs(FiedlerVec),
         Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
  filter(y > 0) %>%
  ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
  stat_ecdf() +
  geom_vline(xintercept = 0.009, lty = 2) +
  theme_classic()
```

@@

Make sure to emphasize that the high overlap between sliding windows makes it more likely that differences are due to noise in the signal, and not strong variability. Like, you wouldn't expect the actual network distribution to shift that much after shifting the time series by 1 minute.g
